\documentclass{wle_cv}

\begin{document}

\maketitle{Willie Loftie-Eaton}

\begin{cvsection}{About}
  I am a Computer Science graduate from Stellenbosch University. In my
  undergraduate studies, I gained experience with a variety of programming
  languages (x86 assembly, C, Java, Python, SQL, HTML \& CSS, and React.js).
  In 2025, I pursued an honours in computer science, focusing more on machine
  learning and computational intelligence (particle swarm optimization and
  evolutionary computation). I want to have a productive career and I'm eager to
  work hard and learn a lot in 2026, either as a software engineer, or machine
  learning engineer.
\end{cvsection}

\begin{cvsection}{Education}
  \noindent\textbf{BSc Hons Computer Science}, Stellenbosch University \hfill 2025
  \begin{adjustwidth}{1em}{0pt}
    Took modules covering \textbf{machine learning} (Dimensionality Reduction,
    Classification, Hidden Markov Models), \textbf{computational intelligence}
    (Particle Swarm Optimization, Genetic Algorithms), \textbf{artificial
    intelligence} (Prolog, Problog, Reinforcement Learning), \textbf{automata
    theory} (Church-Turing Thesis), and \textbf{advanced algorithms}.
  \end{adjustwidth}

  \vspace{0.5em}

  \noindent\textbf{BSc Computer Science}, Stellenbosch University \hfill 2021-2024
  \begin{adjustwidth}{1em}{0pt}
    \noindent 60\% average overall, 65\% average for computer science modules.

    \noindent Took modules covering \textbf{computer science} (DSA, Computer
    Architecture, Web Development, Databases, Networks, Concurrency, Software
    Engineering), \textbf{mathematics} (Calculus, Linear Algebra, Abstract
    Mathematics), \textbf{applied mathematics} (Graph Theory, Cryptography),
    \textbf{operations research} (Queuing Systems), and \textbf{statistics}.
  \end{adjustwidth}

  \vspace{0.5em}

  \noindent\textbf{Matric}, Curro Windhoek Gymnasium High School \hfill
  2016-2020
  \begin{adjustwidth}{1em}{0pt}
    Math 1; Computer Studies 2; Physics 2; Business 2; Afrikaans (1) 3; English
    (2) 3
  \end{adjustwidth}
\end{cvsection}

\begin{cvsection}{Experience}
  \noindent\textbf{Kingly Clark}, Summer Internship \hfill June 2024
  \begin{adjustwidth}{1em}{0pt}
    Wrote e2e tests for a React Native application using Jest. I also worked
    with Docker during this internship.
  \end{adjustwidth}
\end{cvsection}

\begin{cvsection}{Projects}
  \noindent\textbf{\texttt{cilpy}}
  \begin{adjustwidth}{1em}{0pt}
    A library for computational intelligence researchers to study diverse and
    complex problems, including multi-objective and dynamically constrained
    optimization problems.
  \end{adjustwidth}
\end{cvsection}

\begin{cvsection}{Research}
    \href{https://willieloea.github.io/research/pso_for_lsop.pdf}{Particle Swarm Optimization for Large Scale Optimization Problems}

    \href{https://willieloea.github.io/research/monads_in_c.pdf}{Monads in C}
\end{cvsection}

\begin{cvsection}{Skills}
  \noindent\textbf{Programming}: Proficient in Python, C, and Java. Familiar
  with Linux, Docker, Git, SQL, HTML, CSS, and React.js.

  \noindent\textbf{Mathematics}: Good understanding of calculus and linear
  algebra, and an elementary understanding of statistics.

  \noindent\textbf{Languages}: English (native), Afrikaans (native).
\end{cvsection}

\begin{cvsection}{Extracurricular Activities}
Started and lead the \href{https://github.com/su-developer-society}{SU Developer
Society} and organised a cross country running competition in 2022.
\end{cvsection}

\end{document}
